Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-05-31 paper.tex
Restored unix line endings
Fix compile issues

		\textbf{JUMBO & CMLXOM} & http://sourceforge.net/projects/cml/ https://bitbucket.org/wwmm/cmlxom/ & Peter Murray-Rust et al. \\ \hline

@@

 	    \textbf{Chempound (Chem#)} & https://bitbucket.org/chempound & Sam Adams et al. \\ \hline

>>>>

		\textbf{JUMBO \& CMLXOM} & http://sourceforge.net/projects/cml/ https://bitbucket.org/wwmm/cmlxom/ & Peter Murray-Rust et al. \\ \hline

@@

 	    \textbf{Chempound (Chem\#)} & https://bitbucket.org/chempound & Sam Adams et al. \\ \hline
